LabMate: a prospectus for types for MATLAB

### 2024-04-11 writing/IMEKOWC2024/LabMate/paper.tex
[ writing ] vjux

So much for what it is to be a valid matrix type: what does it mean to be a valid matrix \remph{in} such a type?
%
Firstly, a singleton entry matrix must have singleton header lists $[r]$ and $[c]$.
\[\begin{array}[b]{r|c|l}
\; & c \\
\cline{1-2}
r  & e\in E(r,c) & \quad \in \Matrix{R}{C}{E}{[r]}{[c]} \\
\cline{1-2}
\end{array} 
\]

\[\begin{array}{l}
\begin{array}{r|c|c|}
  & \cs_A & \cs_b \\
\hline
&&\\
&A \in & B \in \\
\rs &\Matrix{R}{C}{E}{\rs}{\cs_A} & \Matrix{R}{C}{E}{\rs}{\cs_B} \\
&&\\
\hline
\end{array}\\
\;\;\; \in \Matrix{R}{C}{E}{\rs}{(\cs_A\append\cs_B)}
\end{array}\]

>>>>

So much for what it is to be a valid matrix type: what does it mean to be a valid matrix \remph{in} such a type?

Firstly, a singleton entry matrix must have singleton header lists $[r]$ and $[c]$.
\[\begin{array}[b]{r|c|l}
\; & c \\
\cline{1-2}
r  & e\in E(r,c) & \quad \in \Matrix{R}{C}{E}{[r]}{[c]} \\
\cline{1-2}
\end{array} 
\]

Secondly, to check a horizontal pasting of matrices, we must ensure that the header and entry types match, that the row headers are the same for left and right, and that the column headers can be split into a prefix for the left matrix and a suffix for the right. In other words, the column headers for the whole are the concatenation ($\append$) of the column headers for the parts.
\[\begin{array}{l}
\begin{array}{r|c|c|}
  & \cs_A & \cs_b \\
\hline
&&\\
&A \in & B \in \\
\rs &\Matrix{R}{C}{E}{\rs}{\cs_A} & \Matrix{R}{C}{E}{\rs}{\cs_B} \\
&&\\
\hline
\end{array}\bigskip\\
\;\;\; \in \Matrix{R}{C}{E}{\rs}{(\cs_A\append\cs_B)}
\end{array}\]

Thirdly, vertical pasting is similar, except that it is the row headers which split into prefix and suffix while the column headers are shared.
\[
\begin{array}[c]{r|c|}
  & \cs \\
  \hline
  \;    & \\
  \;    & A \in \\
  \rs_A & \Matrix{R}{C}{E}{\rs_A}{\cs} \\
  \;    & \\
  \hline
  \;    & \\
  \;    & B \in \\
  \rs_B & \Matrix{R}{C}{E}{\rs_B}{\cs} \\
  \;    & \\
  \hline
\end{array}
\in
\begin{array}{l}
\Matrix{R}{C}{E}{\\ \quad (\rs_A\append\rs_B)}{\cs}
\end{array}
\]
